No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-16 R/MSE-manuscript.Rmd
fix typo
change supplement to appendix; increase heading level of objectives; fix plot.margin to avoid cropping figures

# plot explicit documentation of steps or components of MSE processes
# Random Sample MSEs
Freq.plot<-ggplot(freq.data_pub,aes(Explicit,Percent))+
  geom_col()+
  coord_flip() +
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
  scale_x_discrete(
    limits=c("Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"),
    labels=c("Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process")) + theme_bw()

Part.plot<-ggplot(part.data_pub,aes(x=order,y=Percent)) +
  facet_wrap(~Stage,scale="free",ncol=2) + geom_col() +
  scale_fill_manual(values=c("#66CCCC","#006666")) +
  scale_x_continuous(breaks = part.data_pub$order,
                     labels = part.data_pub$Participants)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0)) +
  ylab("Percent")+xlab(NULL)+coord_flip() + theme_bw()

Driver.plot<-ggplot(drive.data_pub,aes(x=order,y=Percent)) +
  geom_col() +
  scale_x_continuous(breaks = drive.data_pub$order,
                     labels = drive.data_pub$Driver)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+
  ylab("Percent")+xlab(NULL)+coord_flip()+ theme_bw()
```

@@

### Objectives 
Our overall objective is to determine the extent that MSE achieves the aspirational aims outlined above, and whether MSE documentation supports learning within the MSE practitioner community.  Given that scientific publication is the primary means of communicating the results of MSE, we review the scientific literature to assess the extent to which the process and aims of MSE, and adaptive management are being achieved and supported by the scientific literature. To assess this, we determine how MSEs utilize standard components of decision making processes. We use the structured decision making (SDM) process [@SDM] -- the decision making framework in which adaptive management occurs -- as our framework for evaluation.  Using this framework, we review published MSEs to:

@@

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019 (Table \@ref(tab:MSEcount)). This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original January 8th, 2019 Web of Science search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 climate change MSE articles published in 2019.

@@

We collected additional information about the MSEs we reviewed beyond what is reported here. For a full description of the information recorded in the relational database see the supplemental information (supplement 1), and for the full data set and results see our shiny application (https://jonathancummings.shinyapps.io/MSEreview/).

@@

### Explore and expand upon this review
To aid learning from the documentation that has occurred, and provide ready access to future MSE documentation we produced a shiny application [@R-Shiny] to enable an interactive means to explore the MSE literature (<https://jonathancummings.shinyapps.io/MSEreview/>). The MSE review shiny application enables user to interactively explore the results presented in this article. The application includes additional analyses that may be of interest, such as an analysis of what journals MSEs have been published in, who is authoring MSEs, and more. Users may also filter by driver, location, species, or other characteristics of MSEs to explore a set of MSEs of interest and relevance to aid learning in the MSE practitioner community. We hope that as MSE are conducted they are entered here so that MSE practitioners can further learn from each other in the future.

>>>>

# plot explicit documentation of steps or components of MSE processes
# Random Sample MSEs
Freq.plot<-ggplot(freq.data_pub,aes(Explicit,Percent))+
  geom_col()+
  coord_flip() +
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
  scale_x_discrete(
    limits=c("Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"),
    labels=c("Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process")) + theme_bw() + theme(plot.margin = margin(0, 0.5, 0, 0.25, "cm"))

Part.plot<-ggplot(part.data_pub,aes(x=order,y=Percent)) +
  facet_wrap(~Stage,scale="free",ncol=2) + geom_col() +
  scale_fill_manual(values=c("#66CCCC","#006666")) +
  scale_x_continuous(breaks = part.data_pub$order,
                     labels = part.data_pub$Participants)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0)) +
  ylab("Percent")+xlab(NULL)+coord_flip() + theme_bw() + theme(plot.margin = margin(0, 0.5, 0, 0.25, "cm"))

Driver.plot<-ggplot(drive.data_pub,aes(x=order,y=Percent)) +
  geom_col() +
  scale_x_continuous(breaks = drive.data_pub$order,
                     labels = drive.data_pub$Driver)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+
  ylab("Percent")+xlab(NULL)+coord_flip()+ theme_bw()+ theme(plot.margin = margin(0, 0.5, 0, 0.25, "cm"))
```

@@

## Objectives 
Our overall objective is to determine the extent that MSE achieves the aspirational aims outlined above, and whether MSE documentation supports learning within the MSE practitioner community.  Given that scientific publication is the primary means of communicating the results of MSE, we review the scientific literature to assess the extent to which the process and aims of MSE, and adaptive management are being achieved and supported by the scientific literature. To assess this, we determine how MSEs utilize standard components of decision making processes. We use the structured decision making (SDM) process [@SDM] -- the decision making framework in which adaptive management occurs -- as our framework for evaluation.  Using this framework, we review published MSEs to:

@@

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019 (Table \@ref(tab:MSEcount)). This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (Appendix B), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (Appendix B). Twelve of these articles came from our original January 8th, 2019 Web of Science search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 climate change MSE articles published in 2019.

@@

We collected additional information about the MSEs we reviewed beyond what is reported here. For a full description of the information recorded in the relational database see the supplemental information (Appendix A), and for the full data set and results see our shiny application (https://jonathancummings.shinyapps.io/MSEreview/).

@@

### Explore and expand upon this review
To aid learning from the documentation that has occurred, and provide ready access to future MSE documentation we produced a shiny application [@R-Shiny] to enable an interactive means to explore the MSE literature (<https://jonathancummings.shinyapps.io/MSEreview/>). The MSE review shiny application enables users to interactively explore the results presented in this article. The application includes additional analyses that may be of interest, such as an analysis of what journals MSEs have been published in, who is authoring MSEs, and more. Users may also filter by driver, location, species, or other characteristics of MSEs to explore a set of MSEs of interest and relevance to aid learning in the MSE practitioner community. We hope that as MSE are conducted they are entered here so that MSE practitioners can further learn from each other in the future.
